---
title: "Peaks I have climbed"
author: "Honorio Valdes"
date: "8/4/2020"
output: html_document
---

## Background

The following map shows a list of peaks that I have climbed. All data was sourced from Peakbagger and can be found in the following link <https://www.peakbagger.com/climber/PeakListC.aspx?cid=17014>. Due to data use rules, I obtained all data manually.

*Note:* It has come to my attention that there has been at least one instance of people submitting this page as their own assignment in Coursera. If you see someone with a different name than the author's submitting this work as their own, please flag the submission as plagiarism.

## Data acquisition
The following code was used for data acquisition.

```{r data}
set.seed(2020-08-04)
data <- read.csv('honorio_peak_data.csv')
```

## Map creation

The following code was used to create the map. Rather than using the conventional OpenStreetMap, OpenTopoMap was used in order to better show the peaks.
```{r map}
library(leaflet)
library(leaflet.providers)
df <- data.frame(latitude=data[,1], longitude=data[,2])

data %>% 
  leaflet() %>% 
  addTiles() %>% 
  addProviderTiles(providers$OpenTopoMap, group='Topo') %>%
  addMarkers(popup=data[,3],clusterOptions=markerClusterOptions())

```